---
title: "Pitch presentation"
author: "Bert Lijnen"
date: "23 September 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

# Assignment and data

The assignment for the data science cours **Developing Data Products** consists of two parts:

- Making and publishing a shiny application  

- Making a reproducible pitch presentation explaining how the shiny app has been made and allowing readers to reproduce it.



The data we have used to make a shiny app is **customer satisfaction data** which comprises:  

- The overall satisfaction score for an amusement park   

- Scores on 4 different satisfaction drivers (satisfaction with the rides, games, waiting times and cleanliness of the park). 

- Objective measures for each respondent: whether the respondent visisted the park on a weekend, the number of children they brought and the distance they have traveled to the park.

The next slide shows a snapshot of the dataset as well as a table summarizing the variables. The data comes from Chapman, C. and McDonnell Feit who use it in their book *R for Marketing Research and Analytics*. 

In our shiny app we have used this dataset to build an interactive table and as well as a multiple regression model to predict the overall satisfaction score.


# Data snapshot and summary

```{r}
# Download the data
sat.df<-read.csv("http://goo.gl/HKnl74")
library(kableExtra)
# show a snapshot
pander::pander(head(sat.df),  split.table=Inf, caption="", missing="") 
# Make a summary table
pander::pander(summary(sat.df), split.table=Inf, caption="", missing="")
```

# Building a shiny app: interactive dataset and predicting overal satisfaction

To develop a multiple regression model for predicting overall satisfaction we have used the 4 satisfaction drivers as predictors. The model is: 

```{r}
model1<-lm(overall~rides+games+wait+clean, data=sat.df)
pander::pander(summary(model1), split.table=Inf, caption="", add.significance.stars=TRUE)
```

# Links to code and output

- Shyny app:  https://bertlijnen.shinyapps.io/customersatisfaction/

- Server code: https://github.com/BLijnen/developing-data-products/blob/master/Server_code.Rmd 

- ui code: https://github.com/BLijnen/developing-data-products/blob/master/ui_code.Rmd 

